Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-27 doc/main_jfm.tex
touched up 3.3

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Calculating the Hydrophobic Force}
\label{subsec:calculating_force}
Once \eqref{eq:SKIE} has been solved for $\sigma$, we need to evaluate
the integrals~\eqref{eq:hydrophobicAttraction}. These integrals involve
the stress \eqref{eq:stress} which contains a singular integral for the
gradient of the double-layer potential. To avoid singular integrals, we
evaluate \eqref{eq:hydrophobicAttraction} using the identities
\begin{align}
  \label{eq:recipforcetorque}
  \FF_i^{\text{hydro}} = \int_{\Gamma_i} \JJ_i \,\dif s,\quad
  T_i^{\text{hydro}}    = \int_{\Gamma_i} 
    (\xx - \aa_i)^{\perp} \cdot \JJ_i  \,\dif s,
\end{align}
where
\begin{align}
  \label{eq:jumpstress1}
  \JJ_{i} = 2\gamma\rho^{-1} \sigma v_i \nnu + 
    2\gamma\rho \frac{d\sigma}{ds} \frac{dv_i}{ds} \nnu -
    2\gamma\rho \frac{d\sigma}{ds} \frac{dv_i}{d\nu} \ttau.
\end{align}
Here, $\ttau$ and $\frac{d}{ds}$ are the unit tangent  and arc length
derivative for $\Gamma_i$, respectively, and
\begin{equation}
\label{eq:uidef}
\begin{aligned}
    u(\xx) &= u_i(\xx) + v_i(\xx),\\
    u_i(\xx) &= \frac{1}{2\pi} \int_{\Gamma_i} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
    \quad \xx \in \mathbb{R}^2.
\end{aligned}
\end{equation}
That is, $v_i(\xx)$ is the double-layer potential~\eqref{eq:HAP_DLP} with 
$\Gamma_i$ excluded from $\bd\Omega$. The advantage in
using \eqref{eq:recipforcetorque} over using \eqref{eq:hydrophobicAttraction} is that the components
$\sigma$, $v_i$, $\frac{d\sigma}{ds}$, and $\frac{dv_i}{ds}$ of $\JJ_i$ are smooth functions,
whereas the components of \eqref{eq:stress} are singular integrals.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Calculating the Hydrophobic Force}
\label{subsec:calculating_force}
Once \eqref{eq:screenedSKIE} has been solved for $\sigma$, we need to
evaluate the integrals~\eqref{eq:hydrophobicAttraction} which are the
HAP forces and torques. These integrals involve the
stress~\eqref{eq:stress} which contains a singular integral for the
gradient of the double-layer potential. To avoid singular integrals, we
first define
\begin{align}
  \label{eq:uidef}
  v_i(\xx) = u(\xx) - u_i(\xx),
\end{align}
where
\begin{align}
  u_i(\xx) &= \frac{1}{2\pi} \int_{\Gamma_i} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
    \quad \xx \in \mathbb{R}^2.
\end{align}
That is, $v_i(\xx)$ is the double-layer potential~\eqref{eq:HAP_DLP}
with $\Gamma_i$ excluded from $\bd\Omega$. Having defined $v_i$, we can
show that
\begin{align}
  \label{eq:recipforcetorque}
  \FF_i^{\text{hydro}} = \int_{\Gamma_i} \JJ_i \,\dif s,\quad
  T_i^{\text{hydro}}    = \int_{\Gamma_i} 
    (\xx - \aa_i)^{\perp} \cdot \JJ_i  \,\dif s,
\end{align}
where
\begin{align}
  \label{eq:jumpstress1}
  \JJ_{i} = 2\gamma\rho^{-1} \sigma v_i \nnu + 
    2\gamma\rho \frac{d\sigma}{ds} \frac{dv_i}{ds} \nnu -
    2\gamma\rho \frac{d\sigma}{ds} \frac{dv_i}{d\nnu} \ttau.
\end{align}
Here, $\ttau$ and $\frac{d}{ds}$ are the unit tangent and arc length
derivative for $\Gamma_i$, respectively, and $\nnu$ is the unit normal.
The advantage in using~\eqref{eq:recipforcetorque} over
using~\eqref{eq:hydrophobicAttraction} is that the components $\sigma$,
$v_i$, $\frac{d\sigma}{ds}$, and $\frac{dv_i}{ds}$ of $\JJ_i$ are smooth
functions, whereas the components of \eqref{eq:stress} are singular
integrals.

%To avoid singular integrals, we
%evaluate~\eqref{eq:hydrophobicAttraction} using the identities
%\begin{align}
%  \label{eq:recipforcetorque}
%  \FF_i^{\text{hydro}} = \int_{\Gamma_i} \JJ_i \,\dif s,\quad
%  T_i^{\text{hydro}}    = \int_{\Gamma_i} 
%    (\xx - \aa_i)^{\perp} \cdot \JJ_i  \,\dif s,
%\end{align}
%where
%\begin{align}
%  \label{eq:jumpstress1}
%  \JJ_{i} = 2\gamma\rho^{-1} \sigma v_i \nnu + 
%    2\gamma\rho \frac{d\sigma}{ds} \frac{dv_i}{ds} \nnu -
%    2\gamma\rho \frac{d\sigma}{ds} \frac{dv_i}{d\nu} \ttau.
%\end{align}
%Here, $\ttau$ and $\frac{d}{ds}$ are the unit tangent  and arc length
%derivative for $\Gamma_i$, respectively, and
%\begin{equation}
%\label{eq:uidef}
%\begin{aligned}
%    u(\xx) &= u_i(\xx) + v_i(\xx),\\
%    u_i(\xx) &= \frac{1}{2\pi} \int_{\Gamma_i} \pderiv{}{\nnu_\yy}
%    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
%    \quad \xx \in \mathbb{R}^2.
%\end{aligned}
%\end{equation}
%That is, $v_i(\xx)$ is the double-layer potential~\eqref{eq:HAP_DLP} with 
%$\Gamma_i$ excluded from $\bd\Omega$. The advantage in
%using \eqref{eq:recipforcetorque} over using \eqref{eq:hydrophobicAttraction} is that the components
%$\sigma$, $v_i$, $\frac{d\sigma}{ds}$, and $\frac{dv_i}{ds}$ of $\JJ_i$ are smooth functions,
%whereas the components of \eqref{eq:stress} are singular integrals.
